Useful R tidbits: Social Networks

### 2022-02-15 _academics/ps753-useful-r-tidbits/ps753-useful-r-tidbits.Rmd
Add isolotes command for igraph

# retrieve the index of isolate nodes
# (nodes with component count of 1 from "components" above)
isolates(gotbook.stat)

>>>>

# retrieve the index of isolate nodes
# (nodes with component count of 1 from "components" above)
isolates(gotbook.stat)
# No direct command in igraph, but can do this:
deg_counts <- igraph::degree(gotbook.ig, loops = FALSE)
length(deg_counts[deg_counts == 0])
